\documentclass[12pt]{book}
\input{preamble}
\title{How to Think Like a Mathematician\footnote{\cite{houston2009}}\\Notes, Exercises, and Intuition}
\author{Idris Raja}
\date{August 2024}

\begin{document}
\maketitle{}
\epigraph{
	Key practical advice for all aspiring mathematicians:
	write mathematics correctly and create your own examples.
}{Kevin Houston}
\tableofcontents
\tcblistof[\section]{definition}{List of Definitions}
% \input{figures/01-triangles}
% \input{figures/02-triangles}
\setcounter{chapter}{2}

\part{Study Skills for Mathematicians}
\chapter{Writing mathematics I}
\epigraph{There is nothing to mathematics\;(writing). All you do is sit down at
	a \LaTeX{} terminal\;(typewriter) and bleed.}
{Ernest Hemingway, paraphrased}


\begin{definition}{Basic Rules}{}
	\begin{enumerate}[label = {(\arabic*)}]
		\item Write in sentences, using proper punctuation.
		\item Keep it simple---short words, short sentences.
	\end{enumerate}
\end{definition}

\begin{definition}{Expressing Yourself Clearly}{}
	\begin{enumerate}[label = {(\arabic*)}]
		\item Explain what you are doing and keep the reader informed.
		\item Explain your assertions---say where it came from.
		\item Say what you mean---be precise verging on pedantic.
	\end{enumerate}
\end{definition}

\begin{definition}{Using Symbols}{}
	\begin{enumerate}[label = {(\arabic*)}]
		\item Prefer words over symbols, but don't eschew symbols.
		\item Equals means equals, don't abuse ``$=$''.
	\end{enumerate}
\end{definition}

\begin{definition}{Finishing Off}{}
	\begin{enumerate}[label = {(\arabic*)}]
		\item Proofread your work. Read through it looking for errors:
		      mathematical, typographical, semantic, grammatical, \ldots.
		\item Reflect on the work after some time away. Think about how to
		      deepen your understanding while also refining the presentation.
	\end{enumerate}
\end{definition}

\chapter{Writing mathematics II}
\epigraph{Mathematics reveals its secrets only to those who approach it with
	pure love, for its own beauty} {Archimedes}

\begin{definition}{Express Yourself Clearly}{}
	\begin{enumerate}[label = {(\arabic*)}]
		\item if you use ``if'', then use ``then''.
		\item Call things by their correct name.
		\item Avoid ``it'' and other ambiguous terms.
	\end{enumerate}
\end{definition}
\begin{definition}{Words and Symbols}{}
	\begin{enumerate}[label = {(\arabic*)}]
		\item Don’t begin sentences with a symbol.
		\item Don't abuse the implication symbol.
		\item Use common symbols and notation.
		\item Define your symbols and notation.
	\end{enumerate}
\end{definition}
\begin{definition}{Good Writing Techniques Applies}{}
	\begin{enumerate}[label = {(\arabic*)}]
		\item Use connecting phrases to compose thoughts.
		\item Use synonyms to avoid boring the reader.
	\end{enumerate}
\end{definition}

\chapter{How to solve problems}
\epigraph{I don't have any magical ability. I look at a problem, play with it,
	work out a strategy.} {Terrance Tao}
\begin{definition}{Polya's 4 Step Plan}{}
	\begin{enumerate}[label = {(\roman*)}]
		\item Understand the problem.
		\item Devise a plan.
		\item Execute the plan.
		\item Look back.
	\end{enumerate}
	From~\cite{polya2014}.
\end{definition}

\begin{definition}{Understanding the Problem}{}
	\begin{enumerate}[label = {(\alph*)}]
		\item understand all the words and symbols in the problem
		\item guess – use your intuition
		\item what do you know about the hypothesis and conclusion?
		\item work backwards and forwards
		\item work with initial and special cases
		\item work with a concrete case
		\item draw a picture
		\item think about a similar problem
		\item find an equivalent problem
		\item solve an easier problem
		\item rewrite in symbols or words
	\end{enumerate}
\end{definition}

\begin{definition}{Devising a Plan}{}
	\begin{enumerate}[label = {(\alph*)}]
		\item break the problem into pieces
		\item find the right level
		\item give things names
		\item systematically choose a method
	\end{enumerate}
\end{definition}

\begin{definition}{Executing the Plan}{}
	\begin{enumerate}[label = {(\alph*)}]
		\item check each step – don’t use intuition
	\end{enumerate}
\end{definition}

\begin{definition}{Looking Back}{}
	\begin{enumerate}[label = {(\alph*)}]
		\item check the answer
		\item find another solution
		\item reflect
	\end{enumerate}
\end{definition}

\part{How to think logically}


% \part{Definitions, Theorems and Proofs}
% \part{Techniques of Proof}
% \part{Mathematics that all Good Mathematicians Need}
% \part{Closing Remarks}

\printbibliography{}
\end{document}
